---
title: "R Notebook"
output: html_notebook
---

1. The test scores for English and Math for a class are given below:
English: 56 75 45 71 62 64 58 80 76 61
Math: 66 70 40 60 65 56 59 77 67 63
(a) Check the correlation between scores assuming that they are normally distributed.
(b) Check the correlation between scores assuming that they are not normally distributed.
 

```{r}
English <- c(56,75,45, 71,62,64,58,80,76,61)
Math <- c(66, 70, 40, 60, 65, 56, 59, 77, 67, 63)
cor.test(English, Math, method="pearson") 
```
```{r}
cor.test(English, Math, method="spearman")
```
2. The airquality dataset contains the daily air quality measurements in New York, from
May to September 1973. Without assuming the data to have normal distribution, test at
α = 0.05 significance level if the monthly ozone density in New York has identical data
distributions from May to September 197
```{r}
head(airquality)
boxplot(Ozone ~ Month, data = airquality)
```
```{r}
kruskal.test(Ozone ~ Month, data = airquality)
```
3. A data science student is using three machine learning algorithms to analyze a given
dataset. She tests her model first with a Decision Tree, secondly with a Logistic Regression and then with a Naive Bayes algorithm. She uses 10-fold Cross Validation for each
model. With this method, she randomly divides her dataset into 10 parts and uses 9 of
those parts for training and reserves one tenth for testing. She repeats this procedure
10 times, each time reserving a different tenth-part for testing. Although the cross validation uses different test sets for each run, she makes sure that the three algorithms get
the same test set. Then, she records the Accuracy for each fold. The accuracy for each
fold of the algorithms are given as follows:
Decision Tree: 75, 79, 69, 78, 65, 87, 74, 81, 77, 85
Logistic Regression: 85, 68, 78, 73, 69, 76, 69, 80, 73, 67
Naive Bayes: 86, 75, 79, 82, 68, 69, 77, 81, 80, 79
(a) Does her comparison experiment has a sampling design or block design?
(b) Can she conclude that any one of the machine learning algorithm is more accurate
than the others?
i. Create vectors for each algorithm. Check the means of the accuracy reported
for the three models.
ii. Create a dataframe for these three vectors.
iii. Run friedman.test command to check the significance of the comparison.
Her experiment has a block design.

```{r}
DT<-c(75, 79, 69, 78, 65, 87, 74, 81, 77, 85)
LR<-c(85, 68, 78, 73, 69, 76, 69, 80, 73, 67)
NB<-c(86, 75, 79, 82, 68, 69, 77, 81, 80, 79)
mean(DT)

mean(LR)

mean(NB)

```
```{r}
DT<-c(75, 79, 69, 78, 65, 87, 74, 81, 77, 85)
LR<-c(85, 68, 78, 73, 69, 76, 69, 80, 73, 67)
NB<-c(86, 75, 79, 82, 68, 69, 77, 81, 80, 79)
Accuracy <- c(DT,LR,NB)
Testnames<- rep(c('DT','LR', 'NB'), each=10, rep =3)
Folds <- as.factor(rep(c(1:10), 3))
data.frame(Accuracy,Testnames,Folds)

```
```{r}
friedman.test(Accuracy, Testnames, Folds)
# friedman.test(Accuracy ~ Testnames | Folds) # another option
```



